---
title: "Linear Mixed Model for dFC Metrics - Quadratic Term for SYNC standardized"
author: 
- name: "Fran Hancock"
  affiliation: Department of Neuroimaging, Institute of Psychiatry, Psychology and Neuroscience, King's College London, London, UK 
date: "`r format(Sys.time(), '%B %d, %Y')`"
fontsize: 14pt
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```
## Relationships between the metrics
### Correlations

We investigated the relationships between all 9 metrics using Spearman correlation. Figure x shows the montonic relationships for RUN 1.
  
```{r,corr_plot,echo=FALSE,message=FALSE}
# R code
library(corrplot)
library(lmerTest)
library(easystats)
library(performance)

library(readxl)
Regtable1 <- read_excel("Regtable1.xlsx")
Regtable2 <- read_excel("Regtable2.xlsx")
Regtable3 <- read_excel("Regtable3.xlsx")
Regtable4 <- read_excel("Regtable4.xlsx")

M=cor(Regtable1, method=c('spearman'))
testRes=cor.mtest(Regtable1, conf.level = 0.95)
#tiff('Figures/Corr_run1')
corrplot(M, p.mat =testRes$p, sig.level=0.05,order='hclust',addrect=2,tl.col ='black', tl.srt = 45,addCoef.col = 'white')
#dev.off()
```

### Linear Mixed effects modelling

As the majority of metrics were statically significant, we performed a linear  mixed effect model with quadratic terns for fixed effects of 8 standardized predictors and random effects of RUN for Integrated Information. We obtained the following model:
  
```{r,lme_model,echo=FALSE, message=FALSE,include=FALSE}

Regtb <- read_excel('Regtable_STD.xlsx')
# generate the model
fm <-lmer(PHI ~ OCC + DUR + META + SYNC +I(SYNC^2) +SPEED + PCC + CHI + CENTROPY + (1|RUN), data=Regtb)
```
```{r,lme_first,echo=FALSE, message=FALSE}
summary(fm)

# produce the ANOVA tables for fixed effects
aov <-anova(fm)
#  random effects via liklihood ratios
ran<-ranova(fm)

```
  
Restricting the model to the parameters with statistical significance we obtained the following model:
  
```{r,lme_final,echo=FALSE, message=FALSE}  
final_model<-lmer(PHI ~ I(SYNC^2) + CENTROPY + CHI +(1|RUN), data=Regtb)
# Display final mdoel

final_model
```
  
  
#### Model Performance
  
We assessed the model performance
  
```{r,lme_performance,echo=FALSE, message=FALSE}
model_performance(final_model)

```
  
  
#### Model Data
  
And summarize the model data 
  
```{r,lme_summary,echo=FALSE, message=FALSE}

r<-report(final_model)
#summary(as.data.frame(r))
summary(final_model)
```
  
  
#### Regression summary
  
In summary 
  
```{r,lme_report,echo=FALSE, message=FALSE}
report(final_model)
writeLines("Satterthwaite's method." )



#writeLines('\n\nDATA TABLE\n')
#data_sum
#sink(file=NULL)

```
  
  
#### Model Quality

We evaluated the quality of the model fit and summarized the results in the following plots:
  
```{r,lme_check,echo=FALSE, message=FALSE}
library(easystats)
library(performance)
library(see)

# check the final model
check_model(final_model,panel=FALSE)
# dev.copy(tiff,'Figures/LME_CHECK.tiff',width= 960,height=960, units='px', pointsize=12)
# dev.off()
```
